\begin{homeworkProblem}
   \subsection{Problem 2a}
   A process that would be ergodic in the mean would be the sampling of numbers
   uniformly over some interval $ [a, b] $, $ a,b \in \mathds{R} $ at each time
   $ t $. This process would also be ergodic in the
   autocorrelation. I will demonstrate it as follows.
   \begin{align*}
   \overline{x(t)} = \frac{b+a}{2}
   \end{align*}
   That is, the time-averaged mean is just the average of the range. This is
   intuitively obvious.
   In the case of an ensemble, it is equally as obvious. Considering a
   sufficiently large ensemble, there will be an equal number of all values
   between $ a $ and $ b $ such that the mean is
   \begin{align*}
      \langle x(t) \rangle
      &= \frac{Ma+M(a+\delta)+M(a+2\delta)+\ldots+M(a+N \delta))}{M(N+1)} \\
      &= \frac{Ma(N+1)}{M(N+1)} + \frac{\delta M \frac{N(N+1)}{2}}{M(N+1)} \\
      &= a + \frac{N \delta}{2}
      \intertext{But, $ b = a + N \delta $. So, $ \frac{b+a}{2} =
      \frac{2a + N \delta}{2} $}
      &= \frac{b+a}{2}
   \end{align*}
This is also ergodic in the autocorrelation. Since the numbers are selected
uniformly at random, each time instant corresponds to an independent sample.
Thus, it is the same to consider a sample point from a time-shifted version of $
x(t) $ (at $ t + t_{n} $, for example) or another sample point $ x^{(j)}(t_{n})
$ from the jth sample function of the ensemble. Thus, the autocorrelation of the
ensemble and of the time sequence must be the same.

\subsection{Problem 2b}
If a noise process is ergodic in the autocorrelation, then that means
\[
   \lim_{T \to \infty} \frac{1}{T} \int_{-T/2}^{T/2} x^{(i)}(t)x^{(i)}(t+
   (t_{2}-t_{1})) dt =
   \int_{-\infty}^{\infty}x_{1}x_{2}p_{2}(x_{1},x_{2}; t_{1},t_{2})
   dx_{1}dx_{2}
\]

If a noise process is ergodic in the mean, then that means that
\[
   \lim_{T \to \infty} \frac{1}{T} \int_{-T/2}^{T/2}
   x^{(i)}(t) dt =
   \lim_{N \to \infty} \frac{1}{N} \sum^{N}_{i=1} x_{1}p_{1}(x_{1}; t_{1}) dx_{1}
\]

So, the assumption is that the noise process is ergodic in the autocorrelation.
In general, the equality of the first pair of integrals does not guarantee the
equality of the second pair of integrals. So, no, just because a noise process
is ergodic in the autocorrelation does not mean that the process is ergodic in
the mean. The logical statement to violate then is the following: ``If the noise
process is ergodic in the autocorrelation, then the noise process is ergodic in
the mean.'' This has the logical form ``P $ \to $ Q''. To prove this false, all
we have to do is find some P for which Q is false. That is, we must find some
process which is ergodic in the autocorrelation but is not ergodic in the mean.

After much struggle (thanks to Arnaud Carignan-Dugas for the assistance), I have
found such an example. Consider the random process consisting of selecting some
number $ a $ with probability 1/2 and another number $ -a $ with probability
1/2. The process will be expressed mathematically as follows:
\[
   x^{(i)}(t) = \begin{cases}
      a &\text{ if } i = 1, \\
      -a &\text{ if } i = 2,
   \end{cases}
   \]
   where $ i $ is a random variable with probability .5 that $ i=1 $ and
   .5 that $ i=2 $.

The time-average for the random process is conditional upon the value of $ i $.
If $ i = 1 $, $ \overline{x^{(1)}(t)} = a $. If $ i = 2 $, $
\overline{x^{(2)}(t)} = -a $. However, the ensemble average $ \langle x(t)
\rangle = 0 $. This is because the ensemble average would be calculated as
\[
   \langle x(t) \rangle = \frac{1}{2}a + \frac{1}{2}(-a) = 0
\]
So, this process is not ergodic in the mean. If it is ergodic in the
autocorrelation then we're good!

The calculation of the time-associated autocorrelation, again, depends on the value of $
i $. If $ i=1 $:
\begin{align*}
   \phi_{x}^{(1)}(\tau) &=
   \lim_{T \to \infty}\frac{1}{T} \int_{-T/2}^{T/2} x^{(1)}(t)x^{(1)}(t+\tau) dt
   \\
   &= \lim_{T \to \infty} \frac{1}{T}\int_{-T/2}^{T/2}a^2 dt \\
   &= a^2
\end{align*}
However, if $ i=2 $
\begin{align*}
   \phi_{x}^{(2)}(\tau) &=
   \lim_{T \to \infty}\frac{1}{T} \int_{-T/2}^{T/2} x^{(2)}(t)x^{(2)}(t+\tau) dt
   \\
   &= \lim_{T \to \infty} \frac{1}{T}\int_{-T/2}^{T/2}(-a)(-a) dt \\
   &= a^2
\end{align*}
However, in the case of the ensemble-associated autocorrelation:
\begin{align*}
   \langle x(t) x(t +\tau) \rangle &= \frac{1}{2}\phi_{x}^{(1)}(\tau) +
   \frac{1}{2} \phi_{x}^{(2)}(\tau) \\
   &= \frac{a^2}{2} + \frac{a^2}{2} \\
   &= a^2
\end{align*}
The ensemble-associated autocorrelation equals the time-associated
autocorrelation for each sample function in the ensemble. Thus, it is not the
case that ergodicity in the autocorrelation implies ergodicity in the mean.
\end{homeworkProblem}
