\begin{homeworkProblem}{Problem 4 (Jackson ed. 3 Problem 3.4a)}

The first thing to realize is that no longer is there azimuthal symmetry in this problem. Thus, $\Phi(r,\theta,\phi) = \sum\limits_{l=0}^\infty \sum\limits_{m=-l}^l (A_{lm} r^l + B_{lm} r^{-(l+1)})Y_{lm}(\theta,\phi)$. I have been given $V(R,\phi)$. Now, I need to use orthogonality and slick mathematical tricks to get my answer into a tractable form. $V(R,\phi)$ alternates sign based on how many ``slices'' the sphere has in it (there are 2n wedges for n slices). Thus, the potential can be expressed in the following form if the sphere is aligned such that at $\phi = 0$ the dividing line between V and -V is along the x-axis and for $\phi \in (0,\pi/n)$ the potential is positive.

\[
\Phi(\Phi,R) =
\begin{cases}
V \quad \phi \in \big(\frac{\pi 2j}{n},\frac{\pi (2j+1)}{n}\big) \\
V \quad \phi \in \big(\frac{\pi (2j+1)}{n},\frac{\pi (2j+2)}{n}\big)
\end{cases}
\text{for $j = 0,1,2,...,n-1$}
\]

Thus, in the usual way, we will use orthogonality to obtain the coefficients in terms of the boundary conditions. Note, though, that this solution will determine $\Phi$ inside of the sphere. Thus, all $B_l$ coefficients must drop out in order that $\Phi$ be normalizable (not divergent at $r=0$.

\begin{align}
	A_{ab} R^k &= \int_0^{2\pi}\int_0^\pi V(R,\phi) Y_{ab}^* \sin\theta d\theta d\phi \nonumber \\
	\intertext{These spherical harmonics, $Y_{km}$ can be expressed in terms of associated Legendre polynomials $P_{lm}$, some constants and a complex exponential by :} \nonumber
	Y_{ab} &= \sqrt{\frac{(2a+1)}{4\pi}\frac{(a-b)!}{(a+b)!}} P_{ab}(\cos\theta) exp(i b\phi) \nonumber \\
	A_{ab} R^k &= \sqrt{\frac{(2a+1)}{4\pi}\frac{(a-b)!}{(a+b)!}} \int_0^{2\pi} V(R,\phi) exp(-i b\phi) d\phi \int_0^\pi  P_{ab}(\cos\theta)\sin\theta d\theta d\phi
\end{align}

To be succinct, the first term will become a constant $\gamma_{ab}$. I will also deal with only solving the first integral for a while. This one deserves some treatment.

\begin{align}
  \int_0^{2\pi} V(R,\phi) exp(-i b\phi) d\phi &= V\sum_{j=0}^{n-1} \Big( \int_{\frac{\pi}{n}(2j)}^{\frac{\pi}{n}(2j+1)} exp(-i b\phi) d\phi - \int_{\frac{\pi}{n}(2j+1)}^{\frac{\pi}{n}(2j+2)} exp(-i b\phi) d\phi \Big) \nonumber
\end{align}

\begin{align}
	&= \frac{iV}{b} \sum\limits_{j=0}^{n-1} \Big( \exp(-ib\frac{\pi}{n}(2j+1)) - \exp(-ib \frac{\pi}{n}(2j)) - \exp(-ib \frac{\pi}{n}(2j+2)) + \exp(-ib \frac{\pi}{n}(2j+1)) \Big) \quad \nonumber \\
	%&\text{} \nonumber \\
	&= \frac{iV}{b} \sum\limits_{j=0}^{n-1} \Big(2\exp(-iA(2j+1)) - \exp(-iA(2j)) -\exp(-iA(2j+2)) \quad\quad \text{,\;Allow $b \frac{\pi}{n} \equiv A$} \nonumber \\
	&= \frac{iV}{b} \Big(2exp(-iA)-1-Exp(-2iA)\big) \sum\limits_{j=0}^{n-1} exp(-2iAj) 
\end{align}

At this time, I will consider the sum over j, since I have isolated it to one term. Substituting the expression for A into the exponential yields: $\sum\limits_{j=0}^{n-1} exp(-2\pi i j \frac{b}{n})$. Performing this sum over n yields the following expression:

\[
exp\big(-2\pi i (b-\frac{b}{n})\big) \frac{\exp(2\pi i b)-1}{\exp(2\pi i \frac{b}{n})-1} \nonumber
\]

Now, b and n are integers. b is the order of the spherical harmonic in the complex exponential term. n is the number of planes that I drive through the z axis. Thus, the fraction in the above expression will return 0 for all b. It also seems that the the same fraction is undefined for whenever $b = \gamma n$ ($\gamma$ being some integer). However, applying L'Hospital's rule to the above expression yields $n$ for the entire sum. Note that in order for $b \gamma n$ to be an integer that n must divide b. Thus, the magnitude of b is lower bounded by n. Physically, this means that for this potential, no value of b (in the spherical harmonics) can exist apart from those that are n or greater or -n and smaller.
\\ \par
Consider now the term in front of the sum in equation 2. If we identify $\exp(-iA)$ as some quantity we will call $x$ this expression can be rewritten as $2x-1-x^2$. This can easily be rewritten as $-(x-1)^2$. 
\begin{align}
x-1 &= \exp(-iA)-1  \nonumber \\
&= \exp(-iA/2)\big(\exp(iA/2)-\exp(-iA/2)\big) \nonumber \\
&= -2i\exp(-iA/2)\sin(A/2) \nonumber \\
&= -2i\exp(-i\pi\frac{b}{n})\sin(\frac{\pi b}{2n}) \nonumber \\
-(x-1)^2 &= 4exp(-2\pi i \frac{b}{n})sin^2(\frac{\pi b}{2 n}) \nonumber
\end{align}

In order that this expression be nonzero, we require that $\sin(\frac{\pi b}{2n})=\sin(\frac{\pi \gamma}{2})$ not equal zero. This expression is zero whenever $\gamma$ is even. Thus, $\gamma$ must be odd. So, I can write b as $(2z+1)n$ where $n$ is the number of slices I put through the z axis and $z$ is some integer which can take on the values $-\text{something},-\text{something}+1,...,0,1,2,...,\text{something else},...$.

Finally, I can rewrite equation 1 as follows:

\[
A_{ab} R^k = \frac{iV}{b} \sqrt{\frac{(2a+1)}{4\pi}\frac{(a-b)!}{(a+b)!}} \int_0^\pi  P_{ab}(\cos\theta)\sin\theta d\theta d\phi
\]

Where b is limited to be odd and a multiple of n. So far, I have not done any work to constrain the values of a. In general, performing that integral to constrain a using $\theta$ (as was done with b using $\phi$) would be difficult as this integral does not have any analytic expression. However, if certain values of $Y_{ab}$ are odd, then we can immediately toss away those combinations of $a$ and $b$. So, consider the following property of the associated Legendre polynomials. $P_{ab}(x) = (-1)^b\frac{(a-b)!}{(a+b)!}P_{ab}(x)$. In order for $P_{ab}$ to be odd, then, it must be the case that $(a-b)!=(a+b)!$. This occurs when $b=0$. But, this can not be any instance of $b$ as $b$ must be odd and a multiple of n. Thus, there are so constraints on the value of $b$. Finally, writing this solution with the usual Legendre parameters $l$ and $m$:

\begin{align}
\Phi(r,\theta,\phi) &= \sum\limits_{l=0}^\infty \sum\limits_{-l \leq m\leq-(2j+1)n }^{ l \geq m \geq (2j+1)n} \Big(\frac{iV}{mR^l} \sqrt{\frac{(2l+1)}{4\pi}\frac{(l-m)!}{(l+m)!}} \int_0^\pi  P_{lm}(\cos\theta)\sin\theta d\theta \Big) r^l Y_{lm}(\theta,\phi) \nonumber \\
&\frac{-(l-n)}{2n} < j < \frac{(l-n)}{2n}\; , \; j \in \mathbb{Z} \nonumber
\intertext{I could use orthonormality conditions to reduce the amount of terms in this sum even more. I could even use the fact that $\Im{V} = 0$. But, it's easier to just leave the expression in this form and apply the orthonormality conditions and the ``reality condition'' once n is fixed.}
\end{align}

We now need to determine the first few cases where terms in this sum are nonzero. Consider the case when $n=0$. Then, no $m$'s can exist. Consider the case when $n=1$. For this case, $m$ can be $1$ (the smallest odd multiple of n) $3$, $5$, etc. as long as $l$ will allow it. So, the first few $(l,m)$'s that survive the sum are $(1,-1)$,$(1,1)$,$(2,-1)$,$(2,1)$,$(3,-3)$,$(3,-1)$,$(3,-1)$,$(3,3)$ , etc. Thus, it seems that the general form of a surviving term goes as $(l,m) = (l,(2i+1)n)$ as long as 
\begin{enumerate}
	\item 2i+1 is less than l+1 or greater than -l-1
	\item i is an integer such as to make (2i+1)n an odd multiple of n
\end{enumerate}
\end{homeworkProblem}